---
title: "Swim Accelerometer Visualization"
author: "Will St. John"
date: "Summer 2023"
output: 
    html_document:
        toc: FALSE
        toc_float: FALSE
---
## Goals
The goal of this project is to display 4 windows:

- Video of an accelerometer session
- X acceleration of that accelerometer session
- Y acceleration of that accelerometer session
- Z acceleration of that accelerometer session

## Layout
The 4 frames will have the following layout:

```{python, echo=FALSE}
temp = [
    '______________________',
    '|                    |',
    '|        video       |',
    '|____________________|',
    '|   x  |   y  |   z  |',
    '|______|______|______|']
for i in temp:
    print(i)
```

As the video plays, the X, Y, and Z windows should display the corresponding acceleration at the given time +/- a few seconds. Since the three plots are touching, the y-axis should only be shown on the left-most pannel.

## Visualizations

```{r, include=FALSE}
library(ggplot2)
library(plotly)
```


```{r}

```

```{python, echo=FALSE}
#import main
import tkinter as tk

```
