---
title: "Swim Accelerometer Visualization"
author: "Will St. John"
date: "Summer 2023"
output: 
    html_document:
        toc: FALSE
        toc_float: FALSE
---
## Goals
The goal of this project is to display 4 windows:

- Video of an accelerometer session
- X acceleration of that accelerometer session
- Y acceleration of that accelerometer session
- Z acceleration of that accelerometer session

## Layout
The 4 frames will have the following layout:

```{python, echo=FALSE}
temp = [
    '______________________',
    '|                    |',
    '|        video       |',
    '|____________________|',
    '|   x  |   y  |   z  |',
    '|______|______|______|']
for i in temp:
    print(i)
```

As the video plays, the X, Y, and Z windows should display the corresponding acceleration at the given time +/- a few seconds. Since the three plots are touching, the y-axis should only be shown on the left-most pannel.

## Visualizations

```{r, include=FALSE}
library(ggplot2)
library(plotly)
library(htmlwidgets)
library(lubridate)
```


```{r}
file <- 'Rec_0614_055549_clean.txt'
df <- read.csv(file, sep = '\t', skip = 1)
head(df)
df$TIME2 <- hms(df$Time)
```

```{r}
p <- ggplot(df, aes(x = Time, y = ax)) +
        geom_point(color = 'steelblue', size = 1) +
        geom_line(color = 'steelblue')
p
```


```{r}
str(df$ax)
str(df$Time)
```

```{python, echo=FALSE}
#import main
import tkinter as tk

```
